What do incoming university students believe about open science practices in

### 2021-02-10 analysis/Manuscript.Rmd
Update Manuscript.Rmd

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. For example, in an attempt to replicate 100 published psychological studies, only 38% were adjudged to have replicated the original result, and the average effect size was half that in the original studies [@opensciencecollaborationEstimatingReproducibilityPsychological2015].

These apparent problems with replicability led to speculation regarding its causes, and a variety of potential solutions being proferred. Some of these potential solutions include more frequently conducting and publishing replication studies [see @brandtReplicationRecipeWhat2014], more transparent reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. In some cases changes to practices have been drastic and widespread: For example, the practice of accepting *Registered Reports* (wherein peer review and in principle acceptance for publication happens *prior* to data collection) was first proposed in 2012 [see @chambersRegisteredReportsPresent2020 for a history] and is already offered by more than 250 journals (https://osf.io/rr/).

>>>>

<!--MP ➔ The paragraph below is an attempt to segue to the aim of our study before getting into the lit review – I'm always of fan of making the general aim of the study clear by the end of the first paragraph. I've summarised the sentiment of the original first two paragraphs a bit (and struck out tangential sentences). I'd suggest this could make the first paragraph of the paper – highlighting the the research context and the gap that is driving our study--> 
The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., Baker, 2016; Chambers & Morey, 2017@[https://osf.io/dmfke/], Harris et al., 2018). In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos (e.g., Chopik, 2018; Grahe et al., 2012, Jekel et al., 2019, Schonbrodt, 2019).  These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
